%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern (6 months)} % Job title
    {Finception} % Organization
    {Bengaluru, India} % Location
    {Jan. 2020 - May. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed the user-interface for both web app and cross platform mobile app (Android and iOS) using React and React Native.}
        \item {Worked with Redux, Sass, Material UI, and Typescript to write reusable and maintainable code.}
        \item {Designed several API microservices using Django, Django REST framework and PostgreSQL database.}
        \item {Utilized Python libraries like Pandas, Numpy, Matplotlib for processing tabular format data.}
        \item {Worked as data science, analyzing and driving insights from the Finshots newsletter mailchimp database using Pandas, Matplotlib, Seaborn.}
        \item {Responsible for deﬁning, developing, and evolving software in a fast paced and agile development environment using the latest software development methods and infrastructure. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Leena AI} % Organization
    {Gurgaon, India} % Location
    {May. 2019 - July. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created a standalone web application from scratch for the HR dashboard allowing HR to schedule, view, re-schedule and delete messages.}
        \item {Integrated the standalone application with Leena AI chatbot for better usability resulting in enhanced HR experience.}
        \item {Implemented Socket.io in Node.js and React for real-time message status and delivery updates.}
        \item {Created and maintained internal react libraries used by the frontend team for faster development.}
        \item {Built modern applications using React, Node, Express and MongoDB and implemented different functionalities for the HR admin.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Opalina Technologies Pvt. Ltd.} % Organization
    {Noida Area, India} % Location
    {June 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designing the architecture of a Recruitment Platform, a web application for conducting tests, based on inputs from the HR Department.}
        \item {Creating REST API handling methods/features for user role 'Test Taker': Test Management (test-taking environment).}
        \item {Used React, Antd, Redux, Cache, and Local Storage.}
      \end{cvitems}
    }

\end{cventries}
