%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Vue.js, Node,js, Progressive Web App, Dialogflow} % Role
    {Nexmo - Multilingual AI voice Interface for Kotak Mahindra Bank (SIH, 2019)} % Event
    {SIH, Bhopal} % Location
    {March. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Successfully improvised Kotak Mahindra Bank's virtual assistant, Keya by giving it multi-lingual voice capability; providing it a better natural language processing and context-based answering capabilities as part of Smart India Hackathon 2019}
      \end{cvitems}
    }
%---------------------------------------------------------
    \cventry
    {Python, Keras, Tensorflow, Computer Vision, Image Classification, Transfer learning, Pre-trained model} % Role
    {Flower Recognition Data Science Competition Hackearth} % Event
    {HackerEarth Competition} % Location
    {Oct. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {React, Redux, Typescript, Node.js, REST API} % Role
    {Coronavirus News, Updates, and Analytic Dashboard} % Event
    {Project} % Location
    {April. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
      \item \href{https://coronavirus2k19.netlify.app/}{Dashboard - \textcolor{mypink}{https://coronavirus2k19.netlify.app/}}
      \item \href{https://ask-me-anything-covid19.netlify.app/}{Chatbot - \textcolor{mypink}{https://ask-me-anything-covid19.netlify.app/}}
      \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {React, Node.js, Express, MongoDB, Flask, Keras, Tensorflow, Machine Learning, NLP, Computer Vision} % Role
    {WeBase - Making Machine Learning Simple} % Event
    {Capstone Project} % Location
    {Aug. 2019 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {WeBase provides common machine learning models as a service to make advance AI accessible for developers. Our simple to use user-interface allows users to use our pre-trained machine learning models with ease.}
        \item {Used NodeJS and Express framework to build server side logic, applied middlewares to handle http requests, connected using MongoDB Atlas. Applied JWT middleware for Authorization. Flask and Keras for deploying, creating and serving ML models.}
        \item {Interpreted 20+ image datasets for image classification algorithms. Extensively worked with transfer learning using pre-trained model.}
        \item {Deployed Deep Learning models on cloud. Frontend on Netlify, Backend (Flask, Node.js) on Heroku. MongoDB Atlas for database. }
        \item {
        \href{https://app-webase.netlify.app/}{Click here for \textcolor{mypink}{Web App Demo}}
        (Test User credentials - harshitsinghai77@gmail.com, password: Pass@12345)
        }
        \item {
        \href{https://app-webase.netlify.app/}{\textcolor{mypink}{Web App}}
        \href{https://webaseai.netlify.app/}{\textcolor{mypink}{Landing Page}}
        \href{https://www.youtube.com/watch?v=buU5tFiB_qQ}{\textcolor{mypink}{Youtube}} \href{https://medium.com/@harshitsinghai77/introducing-webase-3f765076c403}{\textcolor{mypink}{Medium}}
        }. 
      \end{cvitems}
    }

%---------------------------------------------------------

\cventry
    {React, Flask, Keras, TensorFlow, NLP, Computer Vision} % Role
    {Peach Pixel - Turn Design Mockups into HTML Code using Deep Learning} % =Event
    {BML Munjal Hackathon } % Location
    {March, 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
      \item Built web application for front-end automation using deep learning. Engineered a neural network to code a basic HTML, CSS and Bootstrap website based on a picture of a design mockup leading to rapid design prototyping, thus increasing productivity and saving time. \href{https://bit.ly/3hJPp8x}{\textcolor{mypink}{https://bit.ly/3hJPp8x}} 
      \end{cvitems}
    }
%---------------------------------------------------------
    
\end{cventries}
